An event-sourced and decentralized database with IPLD and materialized views

### 2019-09-26 draft.tex
update: adds footnotes for db examples
Signed-off-by: Carson Farmer <carson.farmer@gmail.com>

To make Threads as easy to adopt and use as possible, Textile has designed a public (developer facing) API on top of the Threads internals that simplifies dealing with events and data, while still maintaining the power and flexibility of CQRS and ES. Developers should not have to learn a whole new set of terms and tools to take advantage of Textile's Threads capabilities. These simple, public-facing APIs will be comfortable to application developers looking to leverage highly-distributed systems that connect user-controlled data, with minimal configuration and maximum interoperability. Inspired by tools such as MondoDB [REF], Parse [REF], and Realm [REF], as well as the idea of bounded context and aggregate roots from DDD, we provide simple abstractions and associated framework for performing distributed database operations as if they were local.

>>>>

To make Threads as easy to adopt and use as possible, Textile has designed a public (developer facing) API on top of the Threads internals that simplifies dealing with events and data, while still maintaining the power and flexibility of CQRS and ES. Developers should not have to learn a whole new set of terms and tools to take advantage of Textile's Threads capabilities. These simple, public-facing APIs will be comfortable to application developers looking to leverage highly-distributed systems that connect user-controlled data, with minimal configuration and maximum interoperability. Inspired by tools such as MondoDB\footnote{\url{http://www.mongodb.com}}, Parse\footnote{\url{https://parseplatform.org}}, and Realm\footnote{\url{https://realm.io}}, as well as the idea of bounded context and aggregate roots from DDD, we provide simple abstractions and associated framework for performing distributed database operations as if they were local.
